{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-06 thesis/thesis.tex
fix arabic text style and RTL issue
fix arabic citation with help from ppl who know the language
add an english comment about japanese acks line
ack stanley

\setCJKmainfont{HeiseiMinStd-W5}[Path = ./fonts/]

@@

The community of 15-410 TAs
%having surrounded me pretty much since starting undergrad,
nurtured my love of teaching
well before taking the class myself and well after graduation.
%As skilled as the instructor is,
15-410 could not be the world's best operating systems class
without %TAs
course staff %(staves)
who value thorough grading, the Socratic method,
and empathy to struggling students as much
from year to year as the crew I have known.
It was a blessing to serve, and later to do research, among you all.
Thanks to Wind River for generously
providing CMU with Simics educational licenses.
%I am also grateful
Thanks also to Adam Blank and Miriam Zimmerman
for founding and organizing the class Great Practical Ideas,
which teaches oft-neglected programming skills such as version control and debugging,
which I had the opportunity to teach as head instructor one semester.

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
I also thank those %industry
attendees from each of the PDL Consortium member companies
for their interest %, even in more theoretical work,
and for the enlightening conversations resulting therefrom.
%Thanks to the anonymous OOPSLA reviewer who went the extra mile to read my supplementary proofs
%and urged me to improve the formalism to be more foundational
%(the lack of any stronger criticism a silent vote of confidence for their overall correctness).
Thanks to Nicholas D. Matsakis for the mentorship and collaboration during my two summers as a Rust research intern at Mozilla,
and to the rest of the Rust community as well for their %extremely important
work
bringing better concurrent programs to the world from a different angle.
I thank everyone outside my %immediate
research circle who
%whether at the retreat or otherwise,
insisted how cool my research was for directly helping students --
every such reminder helped me keep my head up during darker times.

@@

日本語を
一緒に
勉強したり、
会話したり、
色々教えてくださったりした
仲間の学習者さんたちと
ネイティブスピーカーさんたちへ、
心から感謝を申し上げます。
外国語を学ぶのは
一生の二番
%充実感
達成感
だと考えます。

>>>>

\setCJKmainfont{HeiseiMinStd-W5}[Path = ./fonts/]
%\newfontfamily\arabicfont{Droid Sans Arabic} % doesn't respond to Script = Arabic :(
%\newfontfamily\arabicfont{LateefGR-Regular}[Path = ./fonts/] % doesn't respond to Script = Arabic :(
\newfontfamily\arabicfont{Amiri-Regular}[Path = ./fonts/, Script = Arabic]

@@

The community of 15-410 TAs
%having surrounded me pretty much since starting undergrad,
has nurtured my love of teaching
since well before I took the class myself.
%and well after graduation.
%As skilled as the instructor is,
15-410 could not be the world's best OS class
without %TAs
course staff's %(staves)
unwavering dedication to
thorough grading, the Socratic method,
and empathy to struggling students.
%as much
%from year to year as the crew I have known.
It was a blessing to serve, and later to do research, among you all.
Thanks especially to Stanley Zhang,
%the 2018 TA who took on the mantle of ensuring
the 2018 TA who who worked with me to ensure
15-410 could keep grading projects with Landslide even after I leave.
Thanks to Wind River for generously
providing
%CMU with
Simics educational licenses.
%I am also grateful
Thanks also to Adam Blank %and Miriam Zimmerman % nah, she said it was just adam
for founding and organizing the class Great Practical Ideas,
which teaches oft-neglected programming skills such as version control and debugging,
which I had the opportunity to teach as head instructor one semester.

I thank the Parallel Data Lab, my research group at CMU,
for supporting me at the PDL retreat every fall,
pushing me to refine my presentation skills and to network with strangers (now familiar faces) from industry.
%I also thank those %industry
I also thank the industry attendees
%from each of the PDL Consortium member companies
for their interest %, even in more theoretical work,
%and for the enlightening conversations resulting therefrom.
and enlightening conversations.
%Thanks to the anonymous OOPSLA reviewer who went the extra mile to read my supplementary proofs
%and urged me to improve the formalism to be more foundational
%(the lack of any stronger criticism a silent vote of confidence for their overall correctness).
Thanks to Nicholas D. Matsakis for the mentorship and collaboration during my two summers as a Rust research intern at Mozilla,
and to the rest of the Rust community as well for their %extremely important
work
bringing better concurrent programs to the world from a different angle.
I thank everyone outside my %immediate
research circle who
%whether at the retreat or otherwise,
insisted how cool my research was for directly helping students --
every such reminder helped me keep my head up during darker times.

@@

% I wrote the below myself, but constructed it carefully to not just convey my feelings accurately
% but also produce intelligible output through google translate, for the sake of 日本語のできない読者の方々。
% (The translation is not perfect, like 達成感 means more my personal sense of accomplishment,
% rather than sounding objective (and consequently, kinda pompous) as it does in google's ouput, but it ain't bad.)
% Of course, since google translate is powered by neural nets and is under active research and development,
% I copy the current output here in case it changes in the future.
%
%%%% I would like to express my sincere gratitude to my fellow learners and native speakers
%%%% who have studied Japanese, talked and taught me variously.
%%%% I think that learning a foreign language is the second most successful achievement of my life.
%
% My own (loose) translation would be more like,
% I am forever grateful to the friends I made through Japanese,
% both my companions in language learning and the native speakers I was able to meet and befriend to begin with,
% who studied together with me, carried on conversations with me,
% and taught me a great variety of things.
% I consider learning a foreign language (*nuance of ongoing process rather than completed achievement)
% to be the second greatest sense of accomplishment I have felt in my life.
日本語を
一緒に
勉強したり、
会話したり、
色々教えてくださったりした
仲間の学習者さんたちと
ネイティブスピーカーさんたちへ、
心から感謝を申し上げます。
外国語を学ぶのは
一生の二番
%充実感
達成感
だと考えます。
